Missing The Point:

### 2020-07-14 ICML/MissingThePoint.Rmd
Add ARTEMISS style files
Added links etc. to ARTEMISS presentation

# Algorithmic Non-Convergence

@@

From an incomplete multivariate normal set ( $n_{\rm obs}=1000, n_{\rm sim} = 1000$ ), we obtain valid regression estimates after 5 to 10 iterations. <!-- Multivariate normal set ( $n = 1000$ ), 'amputed' with a varying proportion of incomplete cases, and 'imputed' with a varying number of iterations. Depicted are the bias and coverage rate of an estimated regression coefficient ( $n_{\rm sim} = 1000$ ). -->

@@

est_Rh <- results %>% ggplot(aes(x = t, y = r.hat.max.beta, color = as.factor(p*100))) +
  geom_hline(yintercept = 1,
             color = "grey",
             lwd = 
               1) +
  geom_point(size = .5, na.rm = TRUE) +
  geom_line(size = .5, na.rm = TRUE) +
  geom_line(aes(x=t, y=thresh1.2), color = "grey", linetype = "dashed", size = .25, na.rm = TRUE) +
  geom_line(aes(x=t, y=thresh1.1), color = "grey", linetype = "dashed", size = .25, na.rm = TRUE) +
  geom_line(aes(x=t, y=thresh1.01), color = "grey", linetype = "dashed", size = .25, na.rm = TRUE) +
  scale_colour_manual(values=paint5) +
  scale_y_continuous(limits = c(1,1.53), breaks = c(1,1.1,1.2,1.3,1.4,1.5)) +
  labs(x = "Number of iterations", 
       y = "$\\widehat{R}$",
       colour = "Miss. (%)") +
  theme_classic() +
  theme(legend.position = "bottom")

@@

>>>>

# Algorithmic Convergence

@@

When imputing an incomplete multivariate normal set ( $n_{\rm obs}=1000$, $m=5$, $n_{\rm sim} = 1000$), we obtain valid regression estimates after 5 to 10 iterations. <!-- Multivariate normal set ( $n = 1000$ ), 'amputed' with a varying proportion of incomplete cases, and 'imputed' with a varying number of iterations. Depicted are the bias and coverage rate of an estimated regression coefficient ( $n_{\rm sim} = 1000$ ). -->

@@

est_Rh <- results %>% ggplot(aes(x = t, y = r.hat.max.beta, color = as.factor(p*100))) +
  geom_hline(yintercept = 1,
             color = "grey",
             lwd = 
               1) +
  geom_point(size = .5, na.rm = TRUE) +
  geom_line(size = .5, na.rm = TRUE) +
  geom_line(aes(x=t, y=thresh1.2), color = "grey", linetype = "dashed", size = .25, na.rm = TRUE) +
  geom_line(aes(x=t, y=thresh1.1), color = "grey", linetype = "dashed", size = .25, na.rm = TRUE) +
  geom_line(aes(x=t, y=thresh1.01), color = "grey", linetype = "dashed", size = .25, na.rm = TRUE) +
  scale_colour_manual(values=paint5) +
  scale_y_continuous(limits = c(1,1.53), breaks = c(1,1.1,1.2,1.3,1.4,1.5)) +
  labs(x = "Number of iterations", 
       y = "Ř", #r'$\\widehat{R}$'
       colour = "Miss. (%)") +
  theme_classic() +
  theme(legend.position = "bottom")

@@

Read more: [github.com/hanneoberman/MissingThePoint](https://github.com/hanneoberman/MissingThePoint).

Or follow my updates on Twitter: [@hioberman](https://twitter.com/hioberman)
